---
title: "fireSense_summary Manual"
author: "Alex Chubaty"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
---

# fireSense_summary Module

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE, results = "hold")

if (!require("Require", quietly = TRUE)) {
  install.packages("Require")
  library(Require)
}
Require("SpaDES.core", require = FALSE, upgrade = FALSE)
```

## Overview

Saves and summarizes `fireSense` burn results. It has two modes (parameter `mode`):

- `"single"` (default): run inside a simulation, after `fireSense`. At `end(sim)` it writes `burnMap_year<end>.tif` and `fireSense_burnSummary.csv` to `outputPath(sim)`.
- `"multi"`: run on its own after several replicates have finished. It finds each replicate's burn map and burn summary and makes figures with `fireSenseUtils::plotBurnSummary()`, `plotCumulativeBurns()` and `plotHistoricFires()`.

## Usage

Single mode needs no setup beyond adding the module to a simulation that includes `fireSense`.

### Plotting and saving

Multi mode:

```{r usage, eval = FALSE}
library(SpaDES.core)

mySim <- simInit(
  times = list(start = 2011, end = 2100),
  modules = list("fireSense_summary"),
  params = list(fireSense_summary = list(
    mode = "multi",
    simOutputPath = "outputs/myStudyArea", ## holds rep01/, rep02/, ...
    studyAreaName = "myStudyArea",
    climateScenario = "CanESM5_SSP370",
    reps = 1L:10L
  )),
  objects = list(rasterToMatch = rasterToMatch),
  paths = list(modulePath = "..")
)
spades(mySim)
```

### Uploading

The replicate files are found either from `outputsDF` (the row-bound `outputs(sim)` of the replicates) or, without it, by searching `simOutputPath/rep*/`; in that case the module stops if a burn map or burn summary is missing.
Historical fires for the comparison figure come from `firePolys` and `ignitionFirePoints`, or are downloaded from the Canadian National Fire Database.

## Parameters

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("fireSense_summary", "..")
knitr::kable(df_params)
```

## Events

- `init`: in single mode, schedules `save_single` at `end(sim)`. In multi mode, does all the work: locates the files and makes the figures.
- `save_single`: writes the burn map and burn summary (single mode only).

### Plotting

Multi mode only. Figures are `.png` files under `simOutputPath`, registered in `outputs(sim)`: burn summaries across replicates, cumulative burns, and simulated versus historical ignitions, escapes and area burned.

### Saving

Single mode only; see `save_single`.

## Data dependencies

### Input data

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("fireSense_summary", "..")
knitr::kable(df_inputs)
```

### Output data

None; results are files on disk.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("fireSense_summary", "..")
knitr::kable(df_outputs)
```

## Links to other modules

Uses `burnMap` and `burnSummary` from `fireSense`.
