---
title: "fireSense_summary"
author: "Alex Chubaty"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, message = FALSE, warning = FALSE, results = "hold")

if (!require("Require", quietly = TRUE)) {
  install.packages("Require")
  library(Require)
}
Require("SpaDES.core", require = FALSE, upgrade = FALSE)
```

# Overview

Summarizes the results of multiple `fireSense` simulations, across multiple study areas, climate scenarios, and replicates.

# Usage

Intended to be used for post-simulation processing of multiple LandR Biomass simulations, following a `LandR-fs` project structure and workflow described and templated in the [`SpaDES.project`](https://github.com/PredictiveEcology/SpaDES.project) package.

## Plotting and saving

Several figures are produced, as `.png` files, and summary rasters are written to disk.

## Uploading

Figures can optionally be uploaded to Google Drive.

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("fireSense_summary", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

Description of the module inputs.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("fireSense_summary", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("fireSense_summary", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Originally developed for *post hoc* use with the `fireSense` suite of wildfire modules.
